---
title: "Power Analysis"
author: "Hayden Spence"
date: "5/14/2020"
output: html_document
---

This R notebook is designed to perform power analyses, particularly for randomized controlled trials (RCTs) and one-way ANOVAs. Power analysis is an important step in the design of experiments, helping researchers to determine the sample size necessary to detect an effect of a given size with a certain degree of confidence. The code uses the pwr package in R, which provides functions for power analysis in a variety of contexts.

The script first performs power analyses for two-sample t-tests, determining the required sample size given a certain effect size and power, estimating the effect size given power and sample size, and estimating power given effect size and sample size. For each analysis, the result is plotted to provide a visual representation of the power curve.

The script then performs similar analyses for one-way ANOVAs, estimating the required sample size, the power, and the effect size, given certain parameters.

This script is useful for researchers who are designing experiments and need to determine appropriate sample sizes or understand the trade-offs between power, effect size, and sample size. By using this script, researchers can ensure their experiments are appropriately powered to detect the effects they are interested in.

Note that we provide effect size and power, therefore n is estimated 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 
## Install and Load pwr package 
 
```{r}
# Load required library
# install.packages("pwr")  # Uncomment this line if the 'pwr' package is not installed
library(pwr)
```

# Power analysis for two-sample t-tests

```{r}
# Define common parameters
effect_size <- 0.56
power <- 0.80
type <- "two.sample"
alternative <- "two.sided"

# Conduct power analysis to estimate sample size
sample_size_estimate <- pwr.t.test(d = effect_size, power = power, type = type, alternative = alternative)

# Plot the power curve
plot(sample_size_estimate, xlab = "Sample Size per group")

# Conduct power analysis to estimate effect size
effect_size_estimate <- pwr.t.test(power = 0.60, n = 75, type = type, alternative = alternative)
plot(effect_size_estimate, xlab = "Sample Size per group")

# Conduct power analysis to estimate power
power_estimate <- pwr.t.test(d = .42, n = 150, type = type, alternative = alternative)
plot(power_estimate, xlab = "Sample Size per group")
```


# Power analysis for one-way ANOVA

```{r}
# Define common parameters
k <- 4
sig.level <- 0.05

# Conduct power analysis to estimate sample size
sample_size_estimate_anova <- pwr.anova.test(f = 0.28, k = k, power = power, sig.level = sig.level)
plot(sample_size_estimate_anova)

# Conduct power analysis to estimate power
power_estimate_anova <- pwr.anova.test(f = 0.30, k = k, n = 45, sig.level = sig.level)
plot(power_estimate_anova)

# Conduct power analysis to estimate effect size
effect_size_estimate_anova <- pwr.anova.test(power = power, k = k, n = 45, sig.level = sig.level)
plot(effect_size_estimate_anova)
```























   




